Simple Wind Models

### 2010-06-10 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4992 ac11df5e-a788-c23b-a8e1-c758c323924d

\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {{\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

@@

\begin{abstract}
Blah
\end{abstract}

@@

[Neglect collisional excitation and de-excitation.  These would
require $n_e > 10^3 \cm{-3}$.  Non-detection of FeI argues against
this.]

In this paper, we will focus on two sets of radiative transitions
associated with the Fe$^+$ and Mg$^+$ ions.  The choice of these
specific low-ions is motivated by our own observations
\citep{rubin10b} but (as described below) these two ions exhibit
the dominant characteristics of the majoriy of low-ions used to study
cool-gas outflows. [word] Therefore, the majority of our results can
be generalized to other transitions that are freuqenly used.

The Mg$^+$ ion, with a single 3s electron in the ground-state,
exhibits an alkali doublet of transitions that are analagous to the
\lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
we present the energy level diagram for the Mg$^+$ ion associated with
the commonly observed \mgiid\ doublet.  In non-relativistic quantum
mechanics, the 2p$^6$3p level is said to be split by spin-orbit
coupling.  This doublet marks the only \ion{Mg}{2} electric-dipole transitions
with wavelengths near 2800\AA.  Furthermore, the transtion connecting
the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ is forbidden by several
selection rules.  Therefore, an absorption to either of the upper
states is followed essentially 100$\%$ of the time by a spontaneous decay to the
ground state.

The physics of the \mgiid\ doublet
is analagous [repeating myself] to the physics of \ion{H}{1}
\lya, and also the \naid\ doublet and many other doublets commonly
studied in the ISM and IGM.  The key quantitative differences are in
the wavelengths of the transitions and, for the calculations of interest
in ths paper, their energy separations.  For \ion{H}{1} \lya, the
separation is sufficiently small $\Delta v = c \Delta E / E \approx 1.3
\mkms$ that most radiative transfer treatments ignore the fact that
\lya\ is a pair of transitions.   This is justified by the fact that
most astrophysical processes have turbulent processes that
significnatly exceed this velocity separation and effectively mix the
two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \mkms$),  
\ion{Na}{1} ($\Delta v \approx 304 \mkms$), and most other doublets
commonly studies the separations are large and demand that the lines
be treated separately.  In terms of the analysis of outflows, the line
separation is especially relevant when the outflow speed matches the
line separation.

Iron exhibits the most complex set of energy levels of the elements
frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
energy levels recorded \citep{iron} and even this is a necessarily
incomplete list.  In this paper, we will focus on 9 of the levels
related to the UV1 mutliplet whose wavelengths lie near 2600\AA\
(Figure~\ref{fig:energy}).  One reason for the complexity of iron is
that the majoriyt of energy levels exhibit fine-structure splitting.
This includes the ground-state which has four fine-structure levels with
excitation energies $T_{\rm ex} = \Delta E / k$ ranging from $\approx
500-1500$\,K.  We label these according to the total angular momentum
of each level $J$, with the ground-state having $J=9/2$.
Transitions between these fine-structure levels are magnetic-dipole
transitions with spontaneous decay times of several hours.  In
principle, these levels can be populated by indirect UV pumping
\citep[e.g][]{sv02,pcb06}, but this would require that the gas lie
close to the source of UV photons (see $\S$~\ref{sec:pump}).  In the
following, we will assume that only the ground-state is populated by
electrons and therefore capable of absorbing photons.

[Comment on UV1 a bit more]

@@

The majority (all?) of observational studies of cool gas outflows in
absorption have focused on intervening, star-forming galaxies.  The
unobscured emisison of these galaxies is a complex combination of
stars and \ion{H}{2} regions that is then modulated by dust and gas
within its ISM.  In terms of the spectral regions studied in this
paper, most stars show a featureless continuum with a few spectral
types showing significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
[Any emission??]  Furthermore, \ion{H}{2} regions are observed to emit
at the \mgiid\ doublet, primarily due to recombinations in the outer
layers.  It is beyond the scope of this paper to properly model this
stellar absorption and \ion{H}{2} region emission, but the reader
should be aeware that they can complicate the observed spectrum,
independent of the effects of a galactic outflow.
In the following, we will simply assume a flat continuum that will
generally be normalized to unit value.  The size of the emitting
region, however, will be allowed to vary. [and also anisotropy? if
not, then say so]

@@

@@

In this section, we explore a simple yet illustrative wind model for
an outflow tuned in part to yield a \ion{Mg}{2} absorption profile
simlar to that observed toward $z<1$, star-forming galaxies
\citep{wcp+09,rubin10b}.  We emphasize, however, that we do not
consider the properties of this wind to be any more physically
motivated than any other choice.

We parameterize the wind through a density law

\begin{equation}
n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2}
\end{equation}
which conserves mass-flux and a velocity law

\begin{equation}
v_r (r) = v_0 r
\end{equation}
which corresponds to a purely radial flow.  Turbulent motions are
characterized by a Doppler parameter $b_{\rm turb}$.  
The wind is isotropic, dust-free, and only extends from an inner
radius $r_{\rm inner}$ to $r_{\rm outer}$.  At the center of the wind
is a source of continuum photons with size $r_{\rm source}$.  Lastly,
we convert the hydrogen density $n_{\rm H}$ to the number density of
Mg$^+$ and Fe$^+$ ions by assuming solar relative abundances with an
absolute metallicity of 1/2 solar and depletion factors of 1/10 and
1/20 for Mg and Fe respectively, i.e.\  $\mnmg = 10^{-5.47} n_{\rm H}$ 
and \nfe=\nmg/2.   
These parameters and their values are summarized in
Table~\ref{tab:fiducial}.  
They were chosen to give a wind with a significant optical depth $\tau
>> 1$ to \mgiia\ and a radial wind speed varying from $v_r \approx 100
- 1000\mkms$.

@@

Using the methodology described in $\S$~\ref{sec:method}, we
propogated photons from the source and through the outflow to an
`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
complex.  In Figure~\ref{fig:fiducial_1dspec}, we present the spectrum
that this observer would record with the unattenuated source spectrum
normalized to unit value.

@@

\input{Tables/tab_fiducial.tex}

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_1d.ps}
\caption{
{\it Left} -- (upper) \ion{Mg}{2} profiles for the fiducial wind model
described in Table~\ref{tab:fiducial} and
Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
characteritic of an outflow with significant absorption blueward of
line center (dashed vertical lines) extending to $v = -1000\mkms$
and signficiant emission redward of line center.  Note
that even though the peak optical depth of the \ion{Mg}{2} transitions
is nearly 30 at $v \approx -70 \mkms$, photons scattered off the outflow
fill in the absorption.
(lower) \ion{Fe}{2} absorption and emission profiles for the UV1
multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
show weaker absorption due to the smaller Fe$^+$ number density and
lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
the emission for \feiia\ is significantly weaker than that of the
\feiib\ and \mgiid\ transitions.  This is because a majority of the
absorbed \feiia\ photons are converted into
\ion{Fe}{2}~$\lambda\lambda 2612, 2632$ photons as observed.
[Mention the emission kinematics?]
}
\label{fig:fiducial_nvt}
\end{figure}

>>>>

\newcommand{\aconfig}{a~$^6$D}
\newcommand{\zconfig}{z~$^6$D$^0$}
\newcommand{\mvr}{v_{\rm r}}
\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {{\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

@@

\begin{abstract}
\begin{itemize}
\item Emission is a generic feature of (nearly) isotropic winds.  This
  emission fills in absorption at $v \approx 0$, significantly
  complicating the absorption-line analysis. 
\end{abstract}

@@

[Table of $f,\lambda,A,\gamma$]

In this paper, we will focus on two sets of radiative transitions
associated with the Fe$^+$ and Mg$^+$ ions, a choice motivated by 
our own observations \citep{rubin10b}.  Although this is a limited
set, the two ions and their transitions have 
characteristics that resemble the properties for the majority of low-ions 
observed in cool-gas outflows. [wording still stinks] Therefore, many
of our results may be generalized to other studies.

The Mg$^+$ ion, with a single 3s electron in the ground-state,
exhibits an alkali doublet of transitions similar to the
\lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
we present the energy level diagram for this 
\mgiid\ doublet.  In non-relativistic quantum
mechanics, the 2p$^6$3p level is said to be split by spin-orbit
coupling which produces the line doublet.  These are the only
\ion{Mg}{2} electric-dipole transitions 
with wavelengths near 2800\AA. Also, the transtion connecting
the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
selection rules.  Therefore, an absorption from
2p$^6$^3s~$\to$~2p$^6$3p 
is followed nearly 100$\%$ of the time by a spontaneous decay to the
ground state and our treatment will ignore any other possibilities
(e.g.\ absorption of a second photon).

The physics of the \mgiid\ doublet
is analagous to the physics of \ion{H}{1}
\lya, the \naid\ doublet, and many other doublets commonly
studied in the ISM and IGM.  These doublets differ only in
the transiton wavelengths and the energy of the doublet separation. 
For \ion{H}{1} \lya, the
separation is sufficiently small ($\Delta v = c \Delta E / E \approx
1.3 \mkms$) that most radiative transfer treatments actually ignore the fact that
there are two transitions.   This is generally a justifiable
assumption because 
most astrophysical processes have turbulent motions that
significantly exceed this velocity separation and effectively mix the
two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \, \mkms$),  
\ion{Na}{1} ($\Delta v \approx 304 \, \mkms$), and most of the other doublets
commonly studied the separations are large and the lines
must be treated separately.  Regarding analysis of outflows, the line
separation plays an important role when the outflow speed $\mvr
\gtrsim \Delta v$.

Iron exhibits the most complex set of energy levels of the elements
frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
energy levels recorded \citep{iron}, and even this is an
incomplete list.  
One reason for the complexity of iron is
that the majority of its configurations exhibit fine-structure splitting.
This includes the ground-state configuration (\aconfig) which is split
into 5 levels with 
excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
$T_{\rm{ex} \approx
500-1500$\,K.  These levels are usually labelled by the total angular momentum
$J$, with the ground-state having $J=9/2$ (Figure~\ref{fig:energy}).  
Transitions between these fine-structure levels are 
forbidden (magnetic-dipole) with spontaneous decay times of several hours.

In this paper, we will focus on transitions between the ground-state
configuration and the levels associated with the \zconfig\
configuration.  This set of transitions are named the
UV1 mutliplet with wavelengths near 2600\AA.
There are two resonance-line transitions (defined to originate in the
true ground-state) associated with this multiplet, \feiid,
corresponding to $\Delta J = 0, -1$.  The solid (green) downward
arrows in Figure~\ref{fig:energy} mark the transitions that connect to
the upper energy levels of the resonance lines.  These transitons can
occur following the absorption of a single photon by the ion in its
ground-state.

The Figure also shows (as dashed downward arrows) two of the
transitions that connect to higher energy levels of the \zconfig\
configuration.  Radiatively, these can only occur after the absorption
of two photons: one to raise the electron from the ground-state to an
excited state and one from the excited state to one of the \zconfig\
levels with $J \le 5/2$.  The excitation of the Fe$^+$ ion by the
absorption of UV photons is termed indirect UV pumping
\citep[e.g][]{sv02,pcb06} and requires the ion to lie
near an intense source of UV photons (see $\S$~\ref{sec:pump}).  In the
following, we will assume that this does not occur and that only the 
true ground-state is populated by electrons.

Our calculations also ignore collisional
processes\footnote{Recombination is also ignored.}, i.e.\ collisional
excitation and de-excitation of the various levels.  For the
fine-structure levels of the \aconfig\ configuration, the excitation
energies are modest ($T_{\rm ex} \sim 1000$\,K) but the critical
density $n_c$ is very large.  For the \aconfig$_{9/2} \to
$\aconfig$_{7/2}$ transition, the critical density $n_c \approx XX
\cm{-3}$.  At these densities, one would predict significant (and
detectable) quantities of \ion{Fe}{1} which has not yet been observed
\citep[see also][]{pcb06}.  The strongest arguement for neglecting
collisions is the general absence of {\it absorption} from the
fine-structure levels of the \aconfig\ configuration.  [Does Kate see
blue-shifted FeII* in absorption?]  This provides an empirical
demonstration that collsioinal excitation is insignificant, and by
inference one may neglect collisional de-excitation.  Meanwhile, the
critical density and excitation energies for \ion{Mg}{2} are $n_c =
??, T_{\rm ex} \approx 50,000$\,K.

@@

Nearly all of the absorption studies on cool-gas outflows 
have focused on intensely, star-forming galaxies.  The
intrinsic emisison of these galaxies is a complex combination of
stars and \ion{H}{2} regions that is then modulated by dust and gas
within the galaxy's ISM.  In terms of the spectral regions studied
here, most stars show a featureless continuum with a few spectral
types showing significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
[Any emission??]  \ion{H}{2} regions, meanwhile, are observed to emit
at the \mgiid\ doublet, primarily due to recombinations in the outer
layers [How about FeII?].  It is beyond the scope of this paper to
properly model the 
stellar absorption and \ion{H}{2} region emission, but the reader
should be aware that they can complicate the observed spectrum,
independent of a galactic outflow.
In the following, we will simply assume a flat continuum 
normalized to unit value.  The size of the emitting
region $r_{\rm source}$, however, is a variable parameter.

@@

[Describe 1D and 3D algorithms]

[Put tests in an Appendix?]

@@

In this section, we explore a simple yet illustrative wind model for
a galactic-scale outflow.  The properties of this wind were tuned, in
part, to yield a \ion{Mg}{2} absorption profile 
simlar to that observed toward $z<1$, star-forming galaxies
\citep{wcp+09,rubin10b}.  We emphasize, however, that we do not
favor this fiducial model over any other wind scenario nor are its
properties any more physically motivated. 
Its primary purpose is to establish a baseline for exploration.

The fiducial wind follows a density law

\begin{equation}
n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2}
\end{equation}
(mass-flux conserving) and a velocity law

\begin{equation}
v_r (r) = v_0 r
\end{equation}
which corresponds to a purely radial flow.  Turbulent motions are
characterized by a Doppler parameter $b_{\rm turb}$.  
The wind is isotropic, dust-free, and extends from an inner wind
radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  At
the center of the wind 
is a homogenous source of continuum photons with size $r_{\rm source}$.  Lastly,
we convert the hydrogen density $n_{\rm H}$ to the number density of
Mg$^+$ and Fe$^+$ ions by assuming solar relative abundances with an
absolute metallicity of 1/2 solar and depletion factors of 1/10 and
1/20 for Mg and Fe respectively, i.e.\  $\mnmg = 10^{-5.47} n_{\rm H}$ 
and \nfe=\nmg/2.   
These normalizations give a wind with a peak optical depth $\tau
>> 1$ to \mgiia\ that becomes optically thin over a velocity range
spanning $v_r \approx 100 - 1000 \, \mkms$.  
All of the parameters are summarized in Table~\ref{tab:fiducial}.

@@

Using the methodology described in $\S$~\ref{sec:method}, we
propogated photons from the source and through the outflow to an
`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
complex.  In Figure~\ref{fig:fiducial_1d}, we present the spectrum
that this observer would record with the unattenuated source spectrum
normalized to unit value.   Consider first the \ion{Mg}{2} profiles;
these show the canonical P-Cygni profiles that characterize a 
source embedded within an outflow.  Strong absorption is evident at
$v < -50 \mkms$ in both transitions and each shows emission at
positive velocities.  For this isotropic and dust-free model, the
total equivalent width of the doublet must be zero
(Table~\ref{tab:fiducial_EW}), i.e.\ every photon
absorbed escapes the system at another energy, primarily at lower
frequency.  The wind simply shuffles photons in frequency space.

Focusing on the \ion{Mg}{2} absorption profiles, one notes they have
similar and non-zero depth even though their $f\lambda$ values differ
by a factor of two.  In absorption line analysis, this is generally
the tell-tale signature of a gas that has a high optical depth (i.e.\
saturated) but only partially covers the emitting source
\citep[e.g.][]{hamman10}.  In this fiducial model, however, the wind
entirely covers the source and the observed behaviour is unrelated to
any partial covering.  Figure~\ref{fig:noemiss}, which compares the
absorption profiles as derived and in the limit where photons are not
re-emitted, shows this explicitly.   One notes that the no-emission
case has a pair of strong absorption lines that absorb all photons at
$v \approx -100 \mkms$, i.e.\ these profiles are simply $\exp(-\tau)$
with $\tau$ given by the curve in Figure~\ref{fig:fiducial_nvt}.  
The actual profile, meanwhile, has been `filled in' at $v \approx -100
\mkms$ by photons scattered and re-emitted by the wind.  An
absorption-line analysis that ignores these effects
\citep[e.g.][]{sato} would systematically underestimate the true optical
depth and falsely conclude partial covering.  [MORE?]
[Dan's analytic calculation here?]

One also notes that the emission profiles of the \mgiid\ doublet
are very similar and have comparable equivalent widths.  In fact the
flux of the \mgiib\ transition even exceeds that for \mgiia.  The
profiles are similar because the absorption is saturated.
Furthermore, the flux from \mgiib\ is greater than that for
\mgiia\ because the wind speed exceeds the velocity separation
of the doublet $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$ such
that the \mgiib\ absorption profile absorbs the red wing of the
\mgiia\ emission profile.  The relative strengths of these emission
lines, therefore, is sensitive to both the optical depth and velocity
extent of the wind.

The bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
majority of the \ion{Fe}{2} UV1 transitions.  Several of these are
shown individually in the velocity plot on the right.  The line
profiles for \feiib\ is very similar to those of the \mgiid\ doublet;
one observes strong absorption to negative velocities and strong
emission at $v > 0 \mkms$ producing the P-Cygni profile.  Splitting
the profile at $v = -50 \mkms$, we measure an equivalent width
$W_{2600}^{\rm abs} = 1.19$\AA\ in absorption and $W_{2600}^{\rm em} =
-0.84$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
equivalent width of $W_{2600}^{\rm TOT} \approx 0.35$\AA.  
[Point out that if $\tau_{2600}$ were higher, than the photons would
likely be more trapped and more would come out as 2626.  Also a
v=0km/s component might make quite a difference.]
In contrast, the \feiia\ resonance line shows much weaker emission and
a much higher total equivalent width ($W_{2586}^{\rm TOT} = XX$\AA).
The differences related directly to Einstein coefficients for the
transitions connecting the upper levels of \feiid\ to the 
fine-structure levels of a~$^6$D.  In the case of \feiib, the
\ion{Fe}{2}~2626 transition that returns to the a~$^6$D$_{7/2}$
excited level has an $\approx 4\times$ smaller coefficient than the
resonance line.  Therefore, the majority of photons absorbed at
$\lambda 2600$ are re-emitted with the same energy and only scatter 
in frequency space around the line.  For \feiia, the transitions to
the a~$^6$D$_{7/2}$ and a~$^6$D$_{5/2}$ levels have comparable and
even larger A coefficients than that to the ground-state.  Therefore,
the majority of photons absorbed at $\lambda 2586$ are re-emitted 
as longer wavelength \ion{Fe}{2}~$\lambda 2612$ or $\lambda 2632$
photons.  [Comment on total EW for 2586?]

[Does the FeII 2600 P-Cygni go away if we increase $\tau_{2600}$?]

[Update the EW values with the new FeII data]

Our algorithm tracks the spatial emissivity of the source+wind
complex as a function of frequency.  Therefore, it is straightforward
to construct surface-brightness maps of the emission yielding a
dataset analagous to intergral-field-unit (IFU) observations.  In
Figure~\ref{fig:fig_fiducial_ifu_mgii}, we present the output for our
fiducial wind model at several velocities relative to the \mgiia\
transition. At $\mvr \le -200 \mkms$, where the wind has an optical
depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
the source contributes significantly to the observed flux.  
At $\mvr=-100 \mkms$, however, the
wind absorbs all photons from the source and the observed emission is
entirely due to photons scattered by the wind.  This
emission significantly exceeds that for $\mvr = -200\mkms$ which
explains the fact that the absorption peaks at a velocity offset from
the peak in the wind's optical depth. [word] At $v_{\rm r} \ge 0
\mkms$,  both the source and wind contribute to the observed emission.

[Spatial cut?]

[FeII emission;  2600 and 2612]

\section{Discussion}

[Are MgII and FeII* emission strict predictions of outflows?  People
have been so focused on absorption.]

@@

\input{Tables/tab_fiducial.tex}
\input{Tables/tab_fiducial_ew.tex}

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_1d.ps}
\caption{
{\it Left} -- (upper) \ion{Mg}{2} profiles for the fiducial wind model
described in Table~\ref{tab:fiducial} and
Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
characteritic of an outflow with significant absorption blueward of
line center (dashed vertical lines) extending to $v = -1000\mkms$
and signficiant emission redward of line center.  Note
that even though the peak optical depth of the \ion{Mg}{2} transitions
is nearly 30 at $v \approx -70 \mkms$, photons scattered off the outflow
fill in the absorption.
(lower) \ion{Fe}{2} absorption and emission profiles for the UV1
multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
show weaker absorption due to the smaller Fe$^+$ number density and
lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
the emission for \feiia\ is significantly weaker than that of the
\feiib\ and \mgiid\ transitions.  This is because a majority of the
absorbed \feiia\ photons are converted into
\ion{Fe}{2}~$\lambda\lambda 2612, 2632$ photons as observed.
[Mention the emission kinematics?]
}
\label{fig:fiducial_1d}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_noemiss.ps}
\caption{
The black curves show the line profiles (absorption and emission) of
the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
model.  These shows the canonical P-Cygni profiles of a source
embedded within an outflow.  Overplotted (red) on each transition is
the predicted absorption profile under the constraint that each
absorbed photon is lost from the system, i.e.\ no scattering or
re-emission.   It is evident that the true profiles have been `filled
in' significantly by light scattered in the wind.  Ignoring this
process, one would model the absorption lines with systematicall lower
optical depth and derive a partial covering. [word]
}
\label{fig:noemiss}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_ifu_mgii.ps}
\caption{
Surface-brightness emission maps around the \mgiia\ transition for the
source+wind complex.  The middel panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2796.35$ and the dotted vertical
curves indicating the velocity slices for the emission maps.  The
source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
pixels at the center.   At $\mvr=-200 \mkms$, the wind has an optical
depth of $\tau_{2796} \approx 1$ such that the source contributes
significantly to the observed flux.  At $\mvr=-100 \mkms$, however, the
wind absorbs all photons from the source and the observed emission is
entirely due to photons scattered by the wind.  Surprisingly, this
emission exceeds that observed at $\mvr = -200\mkms$. At $\mvr \ge 0
\mkms$,  both the source and wind contribute to the observed emission.
}
\label{fig:fiducial_ifu_mgii}
\end{figure}
